Figures to insert in text

### 2018-03-07 Chapters/Chapter02.tex
intro + sdm

The framework has both Kanerva's read and the generalized read. The latter was implemented according to the generalization proposed by professor Paulo Murilo. The generalization brings a parameter $z$, which is the exponent. In this case, the results are floating point instead of integer, which considerably reduces performance. When $z=1$, it is exactly as the Kanerva's read. When $z=0$, it is the Chada's read. We also explored how SDM would behave for different values of $z$.

@@

In this chapter we will explore how the generalized read operation works and whether it may improve SDM behavior. In this case, we understand that SDM behavior will have been improved when the critical distance increases, which means it is able to recognize things with even less clues than before.

@@

Physicist Paulo Murilo observed that the models of Kanerva-read ($z=1$) and Chada-read ($z=0$) were simple variations of the exponent $z$, which suggests experimenting with different values. The results, however, have not yielded performance improvements.  Though for $z \leq 1$ results are comparable to $z=1$, for $z>1$, the system shows a clear deterioration, with a smaller distance to convergence and higher divergence at large-distance reads. This is shown in Figures \ref{fig:murillo-generalization-experiments} and \ref{fig:murillo-generalization-experiments-6reads}.

>>>>

The framework has both Kanerva's read and Murilo's generalized read. The generalization brings a parameter $z$, which is the exponent. In this case, the results are floating point instead of integer, which considerably reduces performance. When $z=1$, it is exactly as the Kanerva's read. When $z=0$, it is the Chada's read. We also explored how SDM would behave for different values of $z$.

@@

In this chapter we will explore how Murilo's generalized read operation works and whether it may improve SDM behavior. In this case, we understand that SDM behavior will have been improved when the critical distance increases, which means it is able to recognize things with even less clues than before.

@@

Murilo observed that the models of Kanerva-read ($z=1$) and Chada-read ($z=0$) were simple variations of the exponent $z$, which suggests experimenting with different values. The results, however, have not yielded performance improvements.  Though for $z \leq 1$ results are comparable to $z=1$, for $z>1$, the system shows a clear deterioration, with a smaller distance to convergence and higher divergence at large-distance reads. This is shown in Figures \ref{fig:murillo-generalization-experiments} and \ref{fig:murillo-generalization-experiments-6reads}.
